---
title: "Activity#09"
author: "Jingcheng Xiao with Tariq Lisse"
date: "2022-11-12"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
echo = TRUE,
warning = FALSE,
message = FALSE,
fig.align = "center"
)
```

```{r loadPackages}
# Load packages
library(rvest)
library(dplyr)
library(readr)
library(ggplot2)
library(tidyr)
```

```{r install trackdown}
devtools::install_github(
repo = "claudiozandonella/trackdown",
build_vignettes = TRUE
)
```

```{r upload,eval = FALSE,include=FALSE}
trackdown::upload_file(
file = "act9.Rmd",
hide_code = TRUE,
rich_text = TRUE,
path_output = "act9.pdf"
)
```

```{r update,eval = FALSE,include=FALSE}

trackdown::update_file(
file = "act9.Rmd",
hide_code = TRUE,
rich_text = TRUE,
path_output = "act9.pdf"
)
```

```{r download,eval = FALSE,include=FALSE}
trackdown::download_file(
file = "act9.Rmd"
)
```

```{r render,eval = FALSE,include=FALSE}

trackdown::render_file(
file = "act9.Rmd"
)
```

```{r getStats}
# ESPN CLE 2022 season stats
espnCLEStats <- read_html(
  x = "https://www.espn.com/nba/team/stats/_/name/cle/cleveland-cavaliers"
) %>%
  html_elements(css = "table") %>%
  html_table()
```

```{r getRoster}
# ESPN CLE 2022 season roster
CLERoster <- read_html(
  x = "https://www.espn.com/nba/team/roster/_/name/cle/cleveland-cavaliers"
) %>%
  html_elements(css = "table") %>%
  html_table()
```

```{r dataWrangling}
# clean roster data
roster <- CLERoster[[1]]
roster <- roster[,-1] %>%
    tidyr::separate(
    col = Name,
    into = c("First", "Last")
  )

# After looking at the list elements, we want elements 1 & 2
# cbind that 2 elements
CLEstats <- cbind(espnCLEStats[[1]], espnCLEStats[[2]])

# Clean ESPN Data ----
# Remove Total Row, Separate Name from Position,
# Make a new full name column
espnScoring <- CLEstats %>%
  filter(Name != "Total") %>%
  tidyr::separate(
    col = Name,
    into = c("First", "Last", "Position")
  ) %>%
  mutate(
    "Player" = paste(First, Last, sep = " "),
    .before = First
  )

# Join roster and stats Data Frames
espnScoring <- inner_join(
  x = espnScoring,
  y = roster,
  by = c("First" = "First", "Position" = "POS")
)
```


```{r dataViz}
# make Plot
ggplot(
  data = espnScoring,
  mapping = aes(x = PTS, y = PER, shape = Position, color = Position)
) +
  geom_point(size = 3, na.rm = TRUE) +
  geom_text(
    mapping = aes(label = paste0(`Last.x`)),
    color = "black",
    nudge_y = -1,
    size = 3,
    na.rm = TRUE
  ) +
  theme_bw() +
  labs(
    x = "Points Per Game",
    y = "Player Efficiency Rating",
    title = "Player Efficiency Rating by CLE Player PTS and Position")

```

The data visualization represents the Player Efficiency Rating of the Cleveland Cavaliers basketball players based on their points and position. Based on the visualization, it is evident that Isaiah Mobley, Donovan Mitchell and Kevin Love have the highest player efficiency ratings. Isaiah Mobley is a forward, Donovan Mitchell is a guard and Kevin Love is also a forward.
